### 2022-01-10 src-latex/parts/20-related-work.tex

@@

Based on the observation that OCR errors necessarily affect the performance of NER approaches applied to historical texts, \cite{huynh2020use}, \cite{martinek2019hybrid} and \cite{marz2021data} have proposed different approaches to reduce their negative impact.

>>>>

Most of the current state-of-the-art OCR systems, like Tesseract \cite{smith2007overview}, OCRopus \cite{breuel2008ocropus} and PERO OCR \cite{kohut2021ts} are based on a pipeline of convolutional neural networks (CNNs) and long short-term memory networks (LSTM). Although this kind of model produces good results on modern texts, it faces several challenges with ancient texts, such as the lack of annotated data for learning, or different transcriptions styles in training data.

\cite{martinek2019hybrid} propose an approach to generate synthetic annotated text for historical OCR training, based on manually collected characters from historical text images. This work propose to train an OCR system based on a CNN-
LSTM network with the synthetic data and then to fine-tune the model with some pages of real historical annotated text. The results show that this approach gives state-of-the-art results.

To overcome the limitations due to different transcription styles in training data, PERO OCR adds a Transcription Style Block layer to a classical model based on a CNN and a Recurrent Neural Network components \cite{kohut2021ts}. This block takes the image of the text and a Transcription Style Identifier as inputs and help the network decide what kind of transcription style to use as output.

@@

Based on the observation that OCR errors necessarily affect the performance of NER approaches applied to historical texts, \cite{huynh2020use} and \cite{marz2021data} have proposed different approaches to reduce their negative impact.
